Meta-analysis of composite outcomes in clinical trials

### 2025-01-29 MSc_poster_template.Rmd
Update MSc_poster_template.Rmd
fig =great remove

```{r standard-plot, out.width='80%', fig.align='center', fig.cap='Great figure!', fig.height=4}
# Load the necessary libraries
library(ggplot2)
library(hrbrthemes)
library(readr)
library(dplyr)
library(reshape2)

>>>>

```{r standard-plot, out.width='80%', fig.align='center', fig.height=4}
# Load the necessary libraries
library(ggplot2)
library(hrbrthemes)
library(readr)
library(dplyr)
library(reshape2)
